A Fully Decentralized Infrastructure for Subscription-based IoT Data Trading

### 2020-07-09 ASRLab_Thesis_Template/thesis/thesis.tex
Adjust typesetting

% ------------------------------------------------
%                   DOI Watermark
% ------------------------------------------------
\usepackage{draftwatermark}  % For DOI watermark
\usepackage{listings, makecell, multirow}

@@

\begin{document}
\ShowDOI{doi:XXXX/NCKU2019XXXXX}

@@

\begin{figure}[!t]
    \centering
    \includegraphics[width=3.in]{img/system_design}
    \caption{The system design of a decentralized data trading infrastructure which consists of data providers, consumers and brokers.}
    \label{fig:system_design}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=15cm]{img/pub_sub_model}
    \caption{The players in data subscription-based trading platform consists of data providers, data consumers and brokers.}
    \label{fig:pub_sub_model}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=15cm]{img/channel_and_key}
    \caption{Within MAM channel, the message publisher has 2 types of key, the encryption keys for content encryption and signature keys for digital signatures. Subscribers can validate the message with signature keys and decrypt messages with encryption keys.}
    \label{fig:channel_and_key}
\end{figure}
\clearpage

@@

@@

\begin{table}[h]
	\caption{The comparison of centralized and decentralized identity model}
	\label{tab:did}
	\begin{tabular}{|c|c|c|}
	\hline
		\textbf{Identity Model} & \textbf{Centralized} & \textbf{Decentralized} \\
		\hline
		Control & Enterprises control identities & Entities control their identities \\
		\hline
		Security & Identity held in a centralized service is a honeypot for cyber attacks & Decentralized identity limits data exposure \\
		\hline
		Portability & Identity is fragmented across enterprises & Identity can be portable across enterprises \\
		\hline
	\end{tabular}
\end{table}

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=3.in]{img/DID_VC}
    \caption{The trusted issuer requests user's DID, then issues a VC with his/hers signature. The user can then present the VC to verifier for signature validation.}
    \label{fig:did_vc}
\end{figure}

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=3.5in]{img/TangleID}
    \caption{To participate the data trading, players are required to have DID document issued by TangleID. The Consumer first need to send a registration request to TangleID to get the MAM channel ID of DID document and a public/private key pair for authentication. When the trade establish, the consumer sends the DID MAM channel ID to provider in order to perform encryption key exchange. The data provider can then retrieve the consumer's public key and encrypt the content with it. After the consumer gets the encrypted message, he/she can decrypt the ciphertext with private key and finally get the encryption key of data product.}
    \label{fig:TangleID}
\end{figure}

\subsection{Enable Automated Trading Process}
\begin{figure*}[t]
    \centering
    \includegraphics[width=4in]{img/smart_contract_mam}
    \caption{The information of identity and data streams are stored on the Tangle with MAM which are all recorded on Product Contracts. Participants can easily retrieve information via Product Contract and proceed trading. For signature validation check and further exchange encryption keys, the MAM channel ID of participants' DID document  are written down, presented in blue color. The orange color stands for the information of data products, which includes the data stream channel/endpoint ID and encryption key certified by broker.}
    \label{fig:smart_contract_mam}
\end{figure*}

Ethereum is a cryptocurrency building on top of a public blockchain-based distributed ledger. It provides the smart contract, which is a protocol for formulating agreement on a blockchain that running on decentralized virtual machines. A smart contract can interact with other contracts, make decisions, store data and transfer cryptocurrency. All the participants in Ethereum can verify and execute the contracts, and once the contract is triggered, it is uninterruptible and will be executed automatically without any third-parties.

@@

@@

\lstdefinestyle{solidity}{
	captionpos=b,
	tabsize=4,
	basicstyle=\scriptsize
}
\lstset{style=solidity}
\begin{lstlisting}[caption={Product Contract data fields}, label={lst:constructor}, frame=single]
contract Product {
    address public broker;
    address public provider;
    bool isBrokerWithdraw;
    bool isProviderWithdraw;
    address[] consumers;

@@

    enum State {Launched, KeyCertified, Finished, Refunded}
    State public state;
}
\end{lstlisting}

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=3.5in]{img/key_upload}
    \caption{To add encryption key to Product Contract, the data provider sends the digest of encryption key and the one that signed with his/hers private key. After the broker receive the request, he/she performs digital signature as well, then write the result to the Product Contract.}
    \label{fig:key_upload}
\end{figure}

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=3.5in]{img/mam_structure}
    \caption{With a seed, users can generate multiple channels, which can then generate multiple endpoints. The IDs of channel and endpoint are the roots of different Merkle trees in MSS. The "central endpoint" are endpoints that has ID, where $endpoint\ ID = channel\ ID$.}
    \label{fig:mam_structure}
\end{figure}

@@

\subsection{Delegate MAM operations to Tangle-accelerator}
\label{section:ta_endpoint}
MAM builds a secure and authenticated communication protocol on top of multiple cryptosystems, which low-level devices need to spend a lot of resources to apply it, and they may not even support built-in libraries in regular operating system. To overcome these concerns, we propose another approach that allows data providers to delegate the MAM operations to Tangle-accelerators, proxy servers with high computation power, which can accelerates the interactions with Tangle while ensuring the privacy of data providers. Fig.~ \ref{fig:ta_struct} shows the structure of Tangle-accelerator, and Fig.~\ref{fig:delegation} shows how data providers can adopt MAM.

\begin{figure}[!t]
    \centering
    \includegraphics[width=3.5in]{img/ta_structure}
    \caption{Tangle-accelerator distribute IOTA api requests to idle IOTA nodes (i.e., full nodes) and provide Proof-of-Work acceleration. It can also cache the requests/responses in a key-value store to shorten response time, and automatically resend requests if failed. Tangle-accelerators also form a firewall for full nodes, which don't need to reveal the IP address to public and reduce the risks of being attacks.}
    \label{fig:ta_struct}
\end{figure}

\begin{figure}[!t]
    \centering
    \includegraphics[width=\linewidth]{img/delegation}
    \caption{Data providers can use MAM in 2 ways: the provider performs MAM operations locally, and the provider delegates MAM operations to Tangle-accelerator.}
    \label{fig:delegation}
\end{figure}

@@

%pic
\begin{figure*}[!t]
    \centering
    \includegraphics[width=\linewidth]{img/MAM_E2EE}
    \caption{The process of E2EE.}
    \label{fig:MAM_E2EE}
\end{figure*}

@@

@@

\begin{figure}[!t]
    \centering
    \includegraphics[width=2.5in]{img/launching_product}
    \caption{The process of launching a product.}
    \label{fig:launching_product}
\end{figure}

\begin{lstlisting}[caption={Functions of hased key update and certified key update}, label={lst:key_certification}, frame=single]
    function addHashedKey(
        string memory _hashedKey
    ) public {
        require(
            msg.sender == provider,
            "Only provider can add hashed key."
        );
        require(
            state == State.Launched,
            "One key has been certified."
        );
        hashedKey = hashedKey;
        emit newHashedKey(hashedKey);
    }

    function addCertifiedKey(
        string memory _certifiedKey
    ) public {
        require(
            msg.sender == broker,
            "Only broker can add certifiedKey."
        );
        require(
            state == State.Launched,
            "One key has been certified."
        );
        certifiedKey = _certifiedKey;
        state = State.KeyCertified;
        emit newCertifiedKey(certifiedKey);
    }
\end{lstlisting}

@@

\begin{figure}[!t]
    \centering
    \includegraphics[width=3.5in]{img/key_exchange}
    \caption{Encryption key exchange process.}
    \label{fig:key_exchange}
\end{figure}

\lstdefinestyle{solidity}{
	captionpos=b,
	tabsize=4,
	basicstyle=\scriptsize
}
\lstset{style=solidity}

\begin{lstlisting}[caption={Add encryption key to data consumers}, label={lst:key_exchange}, frame=single]
    function addEncryptKey(
        address _consumer,
        string memory _encryptKey
    ) public {
        require(
            msg.sender == provider,
            "Only provider can add the encrypted key."
        );
        require(
            consumer2Purchase[_consumer].isKeyAdded == false,
            "Encryption key has been added."
        );
        consumer2Purchase[_consumer].encryptKey = _encryptKey;
        consumer2Purchase[_consumer].isKeyAdded = true;
        emit newEncryptKey(_consumer, _encryptKey);
    }
\end{lstlisting}

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=3.5in]{img/unsubscribe}
    \caption{Once a data consumer launch a unsubscription procedure, he/she is added to unsubscriber list and the Product Contract will distribute the funds to provider, broker and consumers respectively. Then, the data provider will generate a new encryption key and upload it for every remaining subscribers.}
    \label{fig:unsubscribe}
\end{figure}

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=1.5in]{img/refund}
    \caption{Once a data consumer launch a refund procedure, all consumers votes to decide whether they want a refund from data providers. Finally, the establishment of refund is determined by Product Contract after checking the votes is higher than a threshold or not.}
    \label{fig:refund}
\end{figure}

@@

% ------------------------------------------------
%                   Evaluation
% ------------------------------------------------
\newpage
\phantomsection
\chapter{Conclusion}
\pagestyle{plain}

@@

\begin{figure}[!t]
    \centering
    \includegraphics[width=3.in]{img/mam_create}
    \caption{Time cost of MAM creation.}
    \label{fig:mam_create}
\end{figure}

@@

\begin{figure}[!t]
    \centering
    \includegraphics[width=3.in]{img/mam_send}
    \caption{The probability distributed function of time cost for sending a message through MAM.}
    \label{fig:mam_send}
\end{figure}

@@

\begin{figure}[!t]
    \centering
    \includegraphics[width=3.5in]{img/rpi3_pow}
    \caption{Local PoW vs. Remote PoW}
    \label{fig:rpi3_pow}
\end{figure}

@@

\begin{figure}[!t]
    \centering
    \includegraphics[width=3in]{img/mam_vs_e2ee}
    \caption{Compare the performance between MAM and E2EE on Raspberry Pi.}
    \label{fig:mam_vs_e2ee}
\end{figure}

@@

@@

\begin{table*}[h]
	\caption{Gas consumption for each function of Product Contract}
	\label{tab:gas}
	\centering
	\resizebox{0.5\textwidth}{!}{
	\begin{tabular}{|c|c|c|c|}
		\hline
		\textbf{function} & \textbf{sender} & \textbf{Gas used} \\
		\hline
		generate contract & broker & 2558980 \\ 
		subscribe product & consumer & 72259 \\ 
		upload hashed key & provider & 68276  \\ 
		upload encryption key to consumer & provider & 86614 \\ 
		upload certified key & broker & 131535 \\
		update amount of uploaded data & broker & 32157 \\
		unsubscribe & consumer & 8234 \\
		request refund & consumer & 12067 \\
		withdraw & broker & 11313 \\
		\hline
	\end{tabular}
	}
\end{table*}

@@

\begin{table*}[h]
	\caption{Data Price Estimation}
	\label{tab:ether}
	\centering
	\resizebox{0.8\textwidth}{!}{
	\begin{tabular}{|c|c|c|c|c|c|}
		\hline
		\textbf{condition} & \textbf{sender} & \textbf{\makecell{minimum price \\ (Ether)}} & \textbf{\makecell{minimum price \\ (USD)}} & \textbf{\makecell{maximum price \\ (Ether)}} & \textbf{\makecell{maximum price \\ (USD)}} \\
		\hline
		\multirow{2}{*}{\makecell{w/o refund \\ unsubscribe}} & provider & 0.021 & 5.038 & 0.076 & 18.291 \\
		 & consumer & 0.00061 & 0.145 & 0.0022 & 0.527\\
		\hline
		\multirow{2}{*}{w/ refund} & provider & 0.021 & 5.038 & 0.076 & 18.291 \\
		 & consumer & 0.00069 & 0.166 & 0.0025 & 0.603 \\
		\hline
		\multirow{2}{*}{w/ unsubscribe} & provider & 0.021 + 0.002N & 5.038 + 0.497N & 0.076  + 0.007N & 18.291 + 1.806N \\
		 & consumer & 0.00067 & 0.159 & 0.0024 & 0.579 \\
		\hline
		\multirow{2}{*}{\makecell{w/ refund \\ unsubscribe}} & provider & 0.021 + 0.002N & 5.038 + 0.497N & 0.076  + 0.007N & 18.291 + 1.806N\\
		 & consumer & 0.0007 & 0.180 & 0.0027 & 0.655 \\
		\hline
	\end{tabular}
	}
\end{table*}

@@

% ------------------------------------------------
%                   附錄 Appendix
% ------------------------------------------------
\BeginAppendixChapter				% User-defined function
\SetupAppendixNumberingFormat		% User-defined function
\newpage
\phantomsection
\chapter{Title of Appendix A}

Write your Appendix here.

  \section{Dolor sit amet}
    Appendix

>>>>

% ------------------------------------------------
%                   DOI Watermark
% ------------------------------------------------
%\usepackage{draftwatermark}  % For DOI watermark
\usepackage{listings, makecell, multirow}

@@

\begin{document}
%\ShowDOI{doi:XXXX/NCKU2019XXXXX}

@@

\begin{figure}[!t]
    \centering
    \includegraphics[width=5.in]{img/system_design}
    \caption{The system design of a decentralized data trading infrastructure which consists of data providers, consumers and brokers.}
    \label{fig:system_design}
\end{figure}

@@

\begin{figure}[H]
    \centering
    \includegraphics[width=4.5in]{img/pub_sub_model}
    \caption{The players in data subscription-based trading platform consists of data providers, data consumers and brokers.}
    \label{fig:pub_sub_model}
\end{figure}

@@

@@

\begin{figure}
    \centering
    \includegraphics[width=6.5in]{img/channel_and_key}
    \caption{Within MAM channel, the message publisher has 2 types of key, the encryption keys for content encryption and signature keys for digital signatures. Subscribers can validate the message with signature keys and decrypt messages with encryption keys.}
    \label{fig:channel_and_key}
\end{figure}
\clearpage

@@

\begin{table}[h]
	\caption{The comparison of centralized and decentralized identity model}
	\label{tab:did}
	\begin{tabular}{|c|c|c|}
	\hline
		\textbf{Identity Model} & \textbf{Centralized} & \textbf{Decentralized} \\
		\hline
		Control & Enterprises control identities & Entities control their identities \\
		\hline
		Security & \makecell{Identity held in a centralized service \\ is a  honeypot for cyber attacks} & \makecell{Decentralized identity \\ limits data exposure} \\
		\hline
		Portability & \makecell{Identity is fragmented \\ across enterprises} & \makecell{Identity can be portable \\ across enterprises} \\
		\hline
	\end{tabular}
\end{table}

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=4.5in]{img/DID_VC}
    \caption{The trusted issuer requests user's DID, then issues a VC with his/hers signature. The user can then present the VC to verifier for signature validation.}
    \label{fig:did_vc}
\end{figure}

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=5.5in]{img/TangleID}
    \caption{To participate the data trading, players are required to have DID document issued by TangleID. The Consumer first need to send a registration request to TangleID to get the MAM channel ID of DID document and a public/private key pair for authentication. When the trade establish, the consumer sends the DID MAM channel ID to provider in order to perform encryption key exchange. The data provider can then retrieve the consumer's public key and encrypt the content with it. After the consumer gets the encrypted message, he/she can decrypt the ciphertext with private key and finally get the encryption key of data product.}
    \label{fig:TangleID}
\end{figure}
\clearpage

\subsection{Enable Automated Trading Process}
Ethereum is a cryptocurrency building on top of a public blockchain-based distributed ledger. It provides the smart contract, which is a protocol for formulating agreement on a blockchain that running on decentralized virtual machines. A smart contract can interact with other contracts, make decisions, store data and transfer cryptocurrency. All the participants in Ethereum can verify and execute the contracts, and once the contract is triggered, it is uninterruptible and will be executed automatically without any third-parties.

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=5.5in]{img/smart_contract_mam}
    \caption{The information of identity and data streams are stored on the Tangle with MAM which are all recorded on Product Contracts. Participants can easily retrieve information via Product Contract and proceed trading. For signature validation check and further exchange encryption keys, the MAM channel ID of participants' DID document  are written down, presented in blue color. The orange color stands for the information of data products, which includes the data stream channel/endpoint ID and encryption key certified by broker.}
    \label{fig:smart_contract_mam}
\end{figure}
\clearpage

@@

\lstdefinestyle{solidity}{
	numbers=left,
    numbersep=1em,
	captionpos=b,
	tabsize=4,
	basicstyle=\linespread{0.9}\small
}
\lstset{style=solidity}
\begin{lstlisting}[caption={Product Contract data fields}, label={lst:constructor}, frame=single]
contract Product {
    address public broker;
    address public provider;
    bool isBrokerWithdraw;
    bool isProviderWithdraw;
    address[] consumers;

@@

    enum State {Launched, KeyCertified, Finished, Refunded}
    State public state;
}
\end{lstlisting}
\clearpage

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=5.5in]{img/key_upload}
    \caption{To add encryption key to Product Contract, the data provider sends the digest of encryption key and the one that signed with his/hers private key. After the broker receive the request, he/she performs digital signature as well, then write the result to the Product Contract.}
    \label{fig:key_upload}
\end{figure}

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=5.5in]{img/mam_structure}
    \caption{With a seed, users can generate multiple channels, which can then generate multiple endpoints. The IDs of channel and endpoint are the roots of different Merkle trees in MSS. The "central endpoint" are endpoints that has ID, where $endpoint\ ID = channel\ ID$.}
    \label{fig:mam_structure}
\end{figure}
\clearpage

@@

\subsection{Delegate MAM operations to Tangle-accelerator}
\label{section:ta_endpoint}
MAM builds a secure and authenticated communication protocol on top of multiple cryptosystems, which low-level devices need to spend a lot of resources to apply it, and they may not even support built-in libraries in regular operating system. To overcome these concerns, we propose another approach that allows data providers to delegate the MAM operations to Tangle-accelerators, proxy servers with high computation power, which can accelerates the interactions with Tangle while ensuring the privacy of data providers. Fig.~ \ref{fig:ta_struct} shows the structure of Tangle-accelerator, and Fig.~\ref{fig:delegation} shows how data providers can adopt MAM.
\clearpage

\begin{figure}[t]
    \centering
    \includegraphics[width=5.5in]{img/ta_structure}
    \caption{Tangle-accelerator distribute IOTA api requests to idle IOTA nodes (i.e., full nodes) and provide Proof-of-Work acceleration. It can also cache the requests/responses in a key-value store to shorten response time, and automatically resend requests if failed. Tangle-accelerators also form a firewall for full nodes, which don't need to reveal the IP address to public and reduce the risks of being attacks.}
    \label{fig:ta_struct}
\end{figure}

\begin{figure}[b]
    \centering
    \includegraphics[width=\linewidth]{img/delegation}
    \caption{Data providers can use MAM in 2 ways: the provider performs MAM operations locally, and the provider delegates MAM operations to Tangle-accelerator.}
    \label{fig:delegation}
\end{figure}
\clearpage

@@

%pic
\begin{figure}[h]
    \centering
    \includegraphics[width=\linewidth]{img/MAM_E2EE}
    \caption{The process of E2EE.}
    \label{fig:MAM_E2EE}
\end{figure}

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=5in]{img/launching_product}
    \caption{The process of launching a product.}
    \label{fig:launching_product}
\end{figure}
\clearpage

@@

\lstset{style=solidity}
\begin{lstlisting}[caption={Functions of hased key update and certified key update}, label={lst:key_certification}, frame=single]
    function addHashedKey(
        string memory _hashedKey
    ) public {
        require(
            msg.sender == provider,
            "Only provider can add hashed key."
        );
        require(
            state == State.Launched,
            "One key has been certified."
        );
        hashedKey = hashedKey;
        emit newHashedKey(hashedKey);
    }

    function addCertifiedKey(
        string memory _certifiedKey
    ) public {
        require(
            msg.sender == broker,
            "Only broker can add certifiedKey."
        );
        require(
            state == State.Launched,
            "One key has been certified."
        );
        certifiedKey = _certifiedKey;
        state = State.KeyCertified;
        emit newCertifiedKey(certifiedKey);
    }
\end{lstlisting}
\clearpage

@@

\begin{figure}[H]
    \centering
    \includegraphics[width=5.5in]{img/key_exchange}
    \caption{Encryption key exchange process.}
    \label{fig:key_exchange}
\end{figure}
\clearpage

\lstset{style=solidity}
\begin{lstlisting}[caption={Add encryption key to data consumers}, label={lst:key_exchange}, frame=single]
    function addEncryptKey(
        address _consumer,
        string memory _encryptKey
    ) public {
        require(
            msg.sender == provider,
            "Only provider can add the encrypted key."
        );
        require(
            consumer2Purchase[_consumer].isKeyAdded == false,
            "Encryption key has been added."
        );
        consumer2Purchase[_consumer].encryptKey = _encryptKey;
        consumer2Purchase[_consumer].isKeyAdded = true;
        emit newEncryptKey(_consumer, _encryptKey);
    }
\end{lstlisting}

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=5.5in]{img/unsubscribe}
    \caption{Once a data consumer launch a unsubscription procedure, he/she is added to unsubscriber list and the Product Contract will distribute the funds to provider, broker and consumers respectively. Then, the data provider will generate a new encryption key and upload it for every remaining subscribers.}
    \label{fig:unsubscribe}
\end{figure}
\clearpage

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=2.5in]{img/refund}
    \caption{Once a data consumer launch a refund procedure, all consumers votes to decide whether they want a refund from data providers. Finally, the establishment of refund is determined by Product Contract after checking the votes is higher than a threshold or not.}
    \label{fig:refund}
\end{figure}

@@

% ------------------------------------------------
%                   Evaluation
% ------------------------------------------------
\newpage
\phantomsection
\chapter{Evaluation}
\pagestyle{plain}

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=5.in]{img/mam_create}
    \caption{Time cost of MAM creation.}
    \label{fig:mam_create}
\end{figure}

@@

\begin{figure}[H]
    \centering
    \includegraphics[width=5.in]{img/mam_send}
    \caption{The probability distributed function of time cost for sending a message through MAM.}
    \label{fig:mam_send}
\end{figure}

@@

\begin{figure}[H]
    \centering
    \includegraphics[width=5in]{img/rpi3_pow}
    \caption{Local PoW vs. Remote PoW}
    \label{fig:rpi3_pow}
\end{figure}

@@

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=4.5in]{img/mam_vs_e2ee}
    \caption{Compare the performance between MAM and E2EE on Raspberry Pi.}
    \label{fig:mam_vs_e2ee}
\end{figure}
\clearpage

@@

\begin{table}[h]
	\caption{Gas consumption for each function of Product Contract}
	\label{tab:gas}
	\centering
	\resizebox{0.7\textwidth}{!}{
	\begin{tabular}{|c|c|c|c|}
		\hline
		\textbf{function} & \textbf{sender} & \textbf{Gas used} \\
		\hline
		generate contract & broker & 2558980 \\ 
		subscribe product & consumer & 72259 \\ 
		upload hashed key & provider & 68276  \\ 
		upload encryption key to consumer & provider & 86614 \\ 
		upload certified key & broker & 131535 \\
		update amount of uploaded data & broker & 32157 \\
		unsubscribe & consumer & 8234 \\
		request refund & consumer & 12067 \\
		withdraw & broker & 11313 \\
		\hline
	\end{tabular}
	}
\end{table}

@@

\begin{table}[h]
	\caption{Data Price Estimation}
	\label{tab:ether}
	\centering
	\resizebox{0.98\linewidth}{!}{
	\begin{tabular}{|c|c|c|c|c|c|}
		\hline
		\textbf{condition} & \textbf{sender} & \textbf{\makecell{minimum price \\ (Ether)}} & \textbf{\makecell{minimum price \\ (USD)}} & \textbf{\makecell{maximum price \\ (Ether)}} & \textbf{\makecell{maximum price \\ (USD)}} \\
		\hline
		\multirow{2}{*}{\makecell{w/o refund \\ unsubscribe}} & provider & 0.021 & 5.038 & 0.076 & 18.291 \\
		 & consumer & 0.00061 & 0.145 & 0.0022 & 0.527\\
		\hline
		\multirow{2}{*}{w/ refund} & provider & 0.021 & 5.038 & 0.076 & 18.291 \\
		 & consumer & 0.00069 & 0.166 & 0.0025 & 0.603 \\
		\hline
		\multirow{2}{*}{w/ unsubscribe} & provider & 0.021 + 0.002N & 5.038 + 0.497N & 0.076  + 0.007N & 18.291 + 1.806N \\
		 & consumer & 0.00067 & 0.159 & 0.0024 & 0.579 \\
		\hline
		\multirow{2}{*}{\makecell{w/ refund \\ unsubscribe}} & provider & 0.021 + 0.002N & 5.038 + 0.497N & 0.076  + 0.007N & 18.291 + 1.806N\\
		 & consumer & 0.0007 & 0.180 & 0.0027 & 0.655 \\
		\hline
	\end{tabular}
	}
\end{table}

@@
